Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-03-17 strang/paper.tex
final? version

%% \author[0000-0001-8401-030X]{M.~Zingale}
%% \affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
%%        Stony Brook, NY 11794-3800}

%% \author[0000-0003-0439-4556]{M.~P.~Katz}
%% \affiliation{Nvidia Corp}

%% \author[0000-0002-1530-781X]{A.\ Harpole}
%% \affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
%%              Stony Brook, NY 11794-3800}

%% \author[0000-0003-2300-5165]{D.\ E.\ Willcox}
%% \affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

@@

There are several different approaches taken in the literature to
this operator-split reacting system, including some approximations
that make integrating the reaction system computationally less expensive:
\begin{itemize}
\item Evolve $(X_k)$ only.  This neglects temperature evolution
  completely in the burn, only evolving Eq.~\ref{eq:species}.  This is
  the method used in \citet{flash}. \MarginPar{other codes?}

@@

\acknowledgements \castro\ is freely available at
\url{http://github.com/AMReX-Astro/Castro}.  All of the code and
problem setups used here are available in the git repo.  The work at
Stony Brook was supported by DOE/Office of Nuclear Physics grant
DE-FG02-87ER40317.  This material is based upon work supported by the
U.S. Department of Energy, Office of Science, Office of Advanced
Scientific Computing Research and Office of Nuclear Physics,
Scientific Discovery through Advanced Computing (SciDAC) program under
Award Number DE-SC0017955.  This research was supported by the
Exascale Computing Project (17-SC-20-SC), a collaborative effort of
the U.S. Department of Energy Office of Science and the National
Nuclear Security Administration.

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          VODE \citep{vode}
         }

>>>>

\author[0000-0001-8401-030X]{M.~Zingale}
\affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
       Stony Brook, NY 11794-3800}

\author[0000-0003-0439-4556]{M.~P.~Katz}
\affiliation{Nvidia Corp}

\author[0000-0003-2300-5165]{D.\ E.\ Willcox}
\affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

\author[0000-0002-1530-781X]{A.\ Harpole}
\affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
             Stony Brook, NY 11794-3800}

@@

There are several different approaches taken in the literature to
this operator-split reacting system, including some approximations
that make integrating the reaction system computationally less expensive:
\begin{itemize}
\item Evolve $(X_k)$ only.  This neglects temperature evolution
  completely in the burn, only evolving Eq.~\ref{eq:species}.  This is
  the method used in \citet{flash}.

@@

\acknowledgements \castro\ and all of the code used here is freely available at
\url{https://github.com/AMReX-Astro/Castro}.   The work at
Stony Brook was supported by DOE/Office of Nuclear Physics grant
DE-FG02-87ER40317.  This material is based upon work supported by the
U.S. Department of Energy, Office of Science, Office of Advanced
Scientific Computing Research and Office of Nuclear Physics,
Scientific Discovery through Advanced Computing (SciDAC) program under
Award Number DE-SC0017955.  This research was supported by the
Exascale Computing Project (17-SC-20-SC), a collaborative effort of
the U.S. Department of Energy Office of Science and the National
Nuclear Security Administration.

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          VODE \citep{vode}
         }
